%-------------------------
% Resume in Latex
% Author : Yung Hin Tse
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Yung Hin Tse} \\ \vspace{1pt}
    \small 623-396-7519 $|$ 
   {\small{yunghint@asu.edu}} $|$ 
   {\small{linkedin.com/in/thomasyht}} $|$ 
   {\small{Have a U.S. Work Authorization}}
\end{center}

%-----------SUMMARY-----------
\section*{Summary}
\begin{itemize}[leftmargin=*, label={}]
    \item Computer Science and upcoming Mathematics (Stats) undergrad double major at ASU. Skilled in Python, Java, and C/C++ for data-driven solutions. Passionate about applying advanced math and statistics to financial modeling, risk management, and algorithmic trading. Looking for a quantitative research/analyst/developer intern role while remaining open to broader software engineering and AI.
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University, Tempe, AZ}{Expected Grad: Dec. 2028}
      {Bachelor of Science in Computer Science}{GPA: 4.00/4.00} 
    \resumeItemListStart
      \resumeItem{Currently enrolled in \textbf{MITx’s Mathematical Methods for Quantitative Finance}, studying advanced stochastic processes, time series models, and financial mathematics in Python to further strengthen my quant modeling skills.}
    \resumeItemListEnd      
    \resumeSubheading
      {Hong Kong University of Science and Technology, Hong Kong SAR}{Sep. 2021 -- Jan. 2022}
      {Bachelor of Science in Engineering with Extended Major in Artificial Intelligence}{GPA: 3.04/4.00}
    \resumeItemListStart
        \resumeItem{Awards: JUPAS Scholarship (HK\$10,000) (Fall 2021)}
        \resumeItem{Awards: CityU HK Scholarships for Hong Kong Talents - Dean Scholarships (HK\$30,000 per annum)}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
  \begin{description}[leftmargin=0cm, style=unboxed, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item[\textbf{Languages:}] Python, Java, C/C++, SQL (Postgres), JavaScript, HTML/CSS, R, Bash
    \item[\textbf{Frameworks:}] Flask, JQuery, WordPress, Agile, TensorFlow, NLTK, TextBlob, Keras, scikit - learn
    \item[\textbf{Developer Tools:}] Git, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse, Vim
    \item[\textbf{Libraries:}] pandas, NumPy, Matplotlib, Seaborn, RandomForest, SciPy, Solana
    \item[\textbf{Certifications:}] Agile Development, Data Manipulation with Python and SQL, Web Development with Frontend Tools, Quantitative Finance \& Algorithmic Trading in Python
  \end{description}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Changing the World: Personal Secretary} $|$ \emph{Python}}{Jan. 2025 -- Feb. 2025 }
    \resumeItemListStart
        \resumeItem{Collaborated to design and optimize the business model for a personal scheduling app organizing stakeholder meetings that contributed to a 20\% improvement in scheduling efficiency and streamlined user processes.}
        \resumeItem{Leveraged ChatGPT-API and analytics to streamline processes and reduce response time by 35\%.}
    \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{PwC Web3 Global Business Case Challenge}}{Sep. 2023 -- Nov. 2023}
    \resumeItemListStart
        \resumeItem{Secured 1st Runner-up in the Global Business Case Challenge by demonstrating exceptional problem-solving skills and effective teamwork.} 
        \resumeItem{Leveraged analytical proficiency to excel in high-stakes environments, securing PwC Summer internships and advancing key financial and consulting competencies.}
        \resumeItem{Applied advanced knowledge in data security and web3 services, gained through targeted workshops and discussions, to develop more secure decentralized applications and streamline global business operations.}
    \resumeItemListEnd          
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer Intern}{Feb. 2025 -- Present}
      {ClearCast LLC}{}
    \resumeItemListStart
        \resumeItem{Developed and maintained company website, resulting in a 50\% increase in user engagement over six months.}
        \resumeItem{Boosted mapping efficiency by 100\% through advanced Pygame integrations, enabling faster and more accurate real-time simulations.}
        \resumeItem{Collaborated with cross-functional teams to integrate advanced software solutions into autonomous swarm robotics, improving emergency response unit efficiency.}        
    \resumeItemListEnd
    \resumeSubheading
      {STEM Private Tutor}{Jun. 2021 -- Jan. 2022}
      {Hong Kong Tutor Association}{}
    \resumeItemListStart
        \resumeItem{Delivered 200+ hours of one-on-one STEM lessons to 15+ students, increasing average test scores by 20\%, by designing individualized lesson plans and interactive projects.}
    \resumeItemListEnd

\resumeSubHeadingListEnd



\end{document}
